sensiAnPaper1All

### 2015-07-13 sensiAnPaper1All.Rmd
sensitivity analysis contd

  nScenarios <- 100
  #nScenarios <- 10
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_100.rda'))
  load(file=paste0(outFolder,'listOutI1_100.rda'))
  load(file=paste0(outFolder,'listOutI2_100.rda'))

@@

  #3) mixture2 : when resistance to one insecticide in the mixture reached, switch to sole use of the 
  #   other until that too reaches the critical point. Record total time.
  # what I actually need to do is start with mixture find the first critical point
  # (need to know which of the insecticides it is)
  # then I need to go to the single run for the other insecticide & starting at 
  # it's current resistance point find out how many more generations to go
  #inputs : inAndOutI1, inAndOutI2, inAndOutMix

  #resistPointsMix2 <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)

@@

  #in 100 runs for all 3 critical points sequential was better than mix1 all the time

@@

  #in 100 runs only one critical point run combination was mix3 better

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #the mixture one looks superficially similar to the individual ones superimposed
  x11()
  plotallele.freq.andy(listOutMix)
  x11()
  plotallele.freq.andy(listOutI1)
  x11()
  plotallele.freq.andy(listOutI2)

  #check2
  #what is the absolute difference between mix3 & sequential ?
  #looks plausible
  resistDifferenceMix3Seq <- resistPointsMix3 - resistPointsSeq

  #check3 is their a difference between the mix & the individual strategies
  #looks mostly plausible, occasionally there are 0s
  resistDifferenceMix1I1 <- resistPointsMix1 - resistPointsI1
  resistDifferenceMix1I2 <- resistPointsMix1 - resistPointsI2

@@

@@

  treeInput <- rbind( treeInput, resistBetterMix1Seq )
  #todo add other results rows here

@@

### do tree analysis
```{r}
  require(rpart)

  #transpose
  treeInput <- t(treeInput)
  #convert to a dataframe
  treeInput <- data.frame(treeInput)

  treePredictorString <- paste(treePredictors, collapse="+")
  treeResponse <- 'betterMix1Seq_cP0.5'

  #at 0.5 level
  tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
  #getting error number of rows of matrices must match (see arg 2)
  #may be becuase all vals are 0 ??
  #yes when I added some 1s it worked OK
  #treeInput$betterMix1Seq_cP0.5[1:5] <- 1

  #using as.formula
  #tree <- rpart::rpart(as.formula(paste("res ~",argString)), data = inputAndResults, method = 'class')  
  #hardcoded args
  #tree <- rpart(res ~ h.RS1_A0 + h.RS2_0B, data = inputAndResults, method = 'class')
  #tree <- rpart(betterMix1Seq_cP0.5 ~ h.RS1_A0 + h.RS2_0B, data = treeInput, method = 'class')

  plot(tree) #plots tree
  text(tree) #labels tree

    #pruning tree
    #   treePruned <- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])
    #   plot(treePruned) #plots tree
    #   text(treePruned) #labels tree

>>>>

  nScenarios <- 100
  #nScenarios <- 1000
  ## do model runs
  listOutMix <- sensiAnPaperPart( nScenarios, insecticideUsed = 'mixture' )
  listOutI1 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide1' )
  listOutI2 <- sensiAnPaperPart( nScenarios, insecticideUsed = 'insecticide2' )

@@

```{r}
  ## to load previously saved runs, e.g. these that I added 100 onto filename
  load(file=paste0(outFolder,'listOutMix_100_4.rda'))
  load(file=paste0(outFolder,'listOutI1_100_4.rda'))
  load(file=paste0(outFolder,'listOutI2_100_4.rda'))

@@

  #3) mixture2 : when resistance to one insecticide in the mixture reached, switch to sole use of the 
  #   other until that too reaches the critical point. Record total time.
  # what I actually need to do is start with mixture find the first critical point
  # (need to know which of the insecticides it is)
  # then I need to go to the single run for the other insecticide & starting at 
  # it's current resistance point find out how many more generations to go
  #inputs : inAndOutI1, inAndOutI2, inAndOutMix
  resistPointsMix2 <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)

@@

  rowSums(resistBetterMix1Seq)/ncol(resistBetterMix1Seq)
  #100runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #                .25                   .26                   .30   
  #1000runs
  #betterMix1Seq_cP0.1 betterMix1Seq_cP0.25  betterMix1Seq_cP0.5 
  #               .178                  .232                  .238

  ## is mix2 better than sequential ?
  #T/F
  resistBetterMix2SeqBoolean <- resistPointsMix2 > resistPointsSeq
  #convert to 0/1
  resistBetterMix2Seq <- plyr::aaply(resistBetterMix2SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix2Seq) <- gsub('gen','betterMix2Seq', rownames(resistBetterMix2Seq))

  rowSums(resistBetterMix2Seq)/ncol(resistBetterMix2Seq)  
  #1000runs
  #betterMix2Seq_cP0.1 betterMix2Seq_cP0.25  betterMix2Seq_cP0.5 
  #             0.471                0.568                0.551

@@

  #tally runs where mix3 better than seq
  rowSums(resistBetterMix3Seq)/ncol(resistBetterMix3Seq)
  #100runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                  .83                   .75                   .72 
  #1000runs
  #betterMix3Seq_cP0.1 betterMix3Seq_cP0.25  betterMix3Seq_cP0.5 
  #                .794                  .726                  .673

  #check1
  #plot the 2 individual results & the mixture, just to check what is going on
  #the mixture one looks superficially similar to the individual ones superimposed
  #x11()
#   plotallele.freq.andy(listOutMix)
#   #x11()
#   plotallele.freq.andy(listOutI1)
#   #x11()
#   plotallele.freq.andy(listOutI2)

  #I should be able to compare single scenarios
  #yes this works, but not too useful
  # plotallele.freq.andy( list(results=list(listOutMix$results[[1]], listOutI1$results[[1]] )) )
  #this is a modifdeied version of Beths function
  #allowing curtis fig2 to be applied to any scenario
  #plotcurtis_f2_generic( listOutMix$results[[1]], listOutI2$results[[1]], listOutI1$results[[1]] )

  #check2
#   #what is the absolute difference between mix3 & sequential ?
#   resistDifferenceMix3Seq <- resistPointsMix3 - resistPointsSeq
#   
#   #check3 is their a difference between the mix & the individual strategies
#   #looks mostly plausible, occasionally there are 0s
#   resistDifferenceMix1I1 <- resistPointsMix1 - resistPointsI1
#   resistDifferenceMix1I2 <- resistPointsMix1 - resistPointsI2

@@

  # comparing sensitivity inputs to those used by Beth to reproduce curtis fig2
#   inputCurtis <- createInputMatrix(FALSE)
#   inputSensiMix <- listOutMix$input
#   
#   input <- cbind(inputCurtis, inputSensiMix)
#   write.csv(input, file=paste0(outFolder,'inputCurtisSensiCompare.csv'))

@@

  #bind results onto predictors
  treeInput <- rbind( treeInput, resistBetterMix1Seq )
  treeInput <- rbind( treeInput, resistBetterMix2Seq )
  treeInput <- rbind( treeInput, resistBetterMix3Seq )

@@

### do tree analysis
```{r, eval=FALSE}
  require(rpart.plot)

  #transpose
  treeInput <- t(treeInput)
  #convert to a dataframe
  treeInput <- data.frame(treeInput)
  #create string with predictor names in
  treePredictorString <- paste(treePredictors, collapse="+")

  treeResponses <- c( rownames(resistBetterMix1Seq),
                      rownames(resistBetterMix2Seq),
                      rownames(resistBetterMix3Seq) )

  #to do trees & plots for all response variables
  for( treeResponse in treeResponses )
  {
    x11()
    #png(paste0(outFolder,"tree",treeResponse,".png"))

    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
    treePruned <- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])
    #adds in no. scenarios correctly and incorrectly classified
    #prp(tree, extra=1, varlen = 10, main=treeResponse)
    prp(treePruned, extra=1, varlen = 10, main=treeResponse)

    #dev.off()
    savePlot(paste0(outFolder,"tree",treeResponse,".png"), type='png')     
  }

#   treeResponse <- 'betterMix1Seq_cP0.5'
#   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class') 
#   
#   #if get error number of rows of matrices must match (see arg 2)
#   #is because all vals are 0
# 
#   plot(tree) #plots tree
#   text(tree) #labels tree
#   #branch predictors 2 phis & P_2  
#     
#   #for mix3 (resistance to both)
#   x11()
#   treeResponse <- 'betterMix3Seq_cP0.5'
#   tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class')  
#   plot(tree) #plots tree
#   text(tree) #labels tree  
#   
#   #branch predictors 2 phis & P_1
#   
#   #or from rpart.plot
#   #prp(tree)
#   
#   #adds in no. scenarios correctly and incorrectly classified
#   prp(tree, extra=1, varlen = 10, main=treeResponse)
#   savePlot(paste0(outFolder,"tree",treeResponse,".png"), type='png')

  #prp(tree, extra=1,box.col=c("pink","palegreen3")[tree$frame$yval],cex=0.5,yesno.yshift=-2)

    #susanas code
    #pruning tree
    #   treePruned <- prune(tree, cp=tree$cptable[which.min(tree$cptable[,"xerror"]),"CP"])
    #   plot(treePruned) #plots tree
    #   text(treePruned) #labels tree 
    # prp(prunned_tree, extra=1,box.col=c("pink", "palegreen3")[prunned_tree$frame$yval],cex=0.5,yesno.yshift=-2)
